{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis}

### 2025-07-15 Notebook LaTEX/SAGD Under Interpolation/main-2025-07-14.tex
;~;

\newcommand{\cov}{\ensuremath{\operatorname{Cov}}}
\newcommand{\var}{\ensuremath{\operatorname{Var}}}

@@

@@

@@

            \item $\sigma^{(I_k)}$ be another list of i.i.d random variable, 
            \item $\tilde \mu \ge 0$ be a constant that is fixed, 
            \item Let $(L_k)_{k \ge 0}$ a sequence of strictly positive numbers. 

@@

            \item $F$ also satisfies Assumption \ref{ass:sum-of-many-aff-comp} with $\RR^{m \times n}$ matrices: $A^{(1)}, A^{(2)}, \ldots, A^{(n)}$, vectors in $\RR^n$: $(b^{(1)}, \ldots, b^{(n)})$. 

@@

        Then, SNAPG-V2 affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters. 

@@

@@

@@

        Then, SNAPG-V2 vanilla affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions as specified in Definition \ref{def:snapg-v2-proto} with the above parameters. 

@@

    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\;\label{lemma:snagp2-one-step-s1}\\

@@

        \begin{align}\label{ineq:snagp2-one-step-s1-rslt1}

@@

        \begin{align}\label{ineq:snagp2-one-step-s1-rslt2}

@@

            \item Assume $x_{k - 1}, v_{k - 1}$ are in $\left(\ker A^{(i)}\right)^\perp$, let $\bar x \in \left(\ker A^{(i)}\right)^{\perp}$ be arbitrary. 

@@

            &F_i(x_{k}) - F_i(\bar x) 
            + \frac{L_k\alpha_k^2}{2} \left\Vert \bar x - v_k\right\Vert^2
                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}
                \left\Vert v_{k - 1} - \bar x\right\Vert^2
                + \frac{\alpha_k(\tilde\sigma - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
                + \frac{(\alpha_k - 1)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2.

@@

        And when $k = 0$, we have \eqref{ineq:snagp2-one-step-s1-rslt2} as well. 

@@

        Firstly take note that from Lemma \ref{lemma:snagp2-one-step-s1} using the fact that $\Pi^{(i)}$ is a projection matrix it has directly: 
            & F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\left\Vert (I - \Pi^{(i)})( v_{k - 1} - \bar x)\right\Vert^2
            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
                F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\left\Vert v_{k - 1} - \bar x\right\Vert^2
            + \frac{L_k}{2}\left\Vert \Pi^{(i)}(z_k - y_k)\right\Vert^2
                + \frac{\alpha_k(\tilde\mu - \sigma^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
        Next, we will show that $\Pi^{(i)}(z_k - y_k)$ is zero under item (i), (ii). 

@@

        Let's prove (i) first. 
        Since $A^{(i)} = I$, its kernel is zero hence the $\Pi^{(i)}$ in Lemma \ref{lemma:snagp2-one-step-s1} projects to $\{0\}$ and the term $\Pi^{(i)}(z_k - y_k) = \mathbf 0$ in \eqref{ineq:snagp2-one-step-s1-rslt1}. It's done. 

@@

        To see (ii), recall that $z_k = \alpha_k \bar x + (1 - \alpha_k) x_{k - 1}$ from Lemma \ref{lemma:snagp2-one-step-s1}, obviously $z_k \perp \ker A^{(i)}$ as well. 
        Recall that $y_k$ as defined in Definition \ref{def:snapg-v2-proto} has
            y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}.
        So $y_k \perp \ker A^{(i)}$ because it's the linear combinations of $v_{k - 1}, x_{k - 1}$. 
        Hence, the projection of $y_k, z_k$ onto $\ker A^{(i)}$ by $\Pi^{(i)}$ is zero, hence the results from Lemma \ref{lemma:snagp2-one-step-s1} simplifies as well. 

@@

    % The following lemma state the relationships of the iterates generated by SNAPG-V2. 
    % They are needed for the convergence proof. 
    % % --------------------------------------------------------------------------------------------------------------
    % \begin{lemma}[properties of the iterates \textcolor{red}{DEPRECATED}]\label{lemma:snapg2-itrs-props}
    %     Suppose that the iterates $(z_k, x_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k)_{k \ge 1}$ are produced by an algorithm satisfying Definition \ref{def:snapg-v2}. 
    %     Let $\bar x \in \RR^n$.
    %     Define the sequence $z_k = \alpha_k\bar x + (1 - \alpha_k)x_{k - 1}$. 
    %     Then, the following are true: 
    %     \begin{enumerate}
    %         \item\label{lemma:snapg2-itrs-props-item1} For all $k \ge 1$ it has: 
    %         \begin{align*}
    %                 z_k - y_k 
    %                 = 
    %                 \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
    %                 + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
    %         \end{align*}
    %         \item\label{lemma:snapg2-itrs-props-item2} For all $k \ge 1$, it has: $z_k - x_k = \alpha_k(x - \bar x)$
    %     \end{enumerate}
    % \end{lemma}
    % \begin{proof}
    %     \textbf{Proof of \ref{lemma:snapg2-itrs-props-item1}}. 
    %     From Definition \ref{def:snapg-v2}, it has
    %     \begin{align*}
    %         (1 + \tau_k)^{-1}
    %         &=
    %         \left(
    %             1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
    %         \right)^{-1} = \left(
    %             \frac{L_k\alpha_k - \mu^{(i)} + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}}
    %         \right)^{-1}
    %         = \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}. 
    %     \end{align*}
    %     Therefore, for all $k \ge 0$, $y_k$ has 
    %     \begin{align*}
    %         0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
    %         \\
    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} 
    %         \left(
    %             v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu^{(i)}} x_{k - 1}
    %         \right) - y_k
    %         \\
    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1}
    %         + \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1} - y_k
    %         \\
    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
    %         + 
    %         \left(
    %             \frac{L_k(1 - \alpha_k)}{L_k - \mu^{(i)}} - (1 - \alpha_k)
    %         \right) x_{k - 1} - y_k
    %         \\
    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
    %         + 
    %         (1 - \alpha_k)\left(
    %             \frac{L_k - L_k + \mu^{(i)}}{L_k - \mu^{(i)}}
    %         \right) x_{k - 1} - y_k
    %         \\
    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} + (1 - \alpha_k)x_{k - 1}
    %         + 
    %         \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}x_{k - 1} - y_k. 
    %     \end{align*}
    %     Therefore, we establish the equality 
    %     \begin{align*}
    %         (1 - \alpha_k)x_{k - 1} - y_k &= 
    %         - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}. 
    %     \end{align*}
    %     On the second equality below, we will the above equality, it goes: 
    %     \begin{align*}
    %         z_k - y_k &= 
    %         \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
    %         \\
    %         &= \alpha_k \bar x 
    %         - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}} v_{k - 1} 
    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
    %         \\
    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
    %         + \left(
    %             \alpha_k - \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}
    %         \right)\bar x
    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
    %         \\
    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
    %         + \left(
    %             \frac{\alpha_kL_k - \alpha_k \mu^{(i)} - L_k\alpha_k + \mu^{(i)}}{L_k - \mu^{(i)}}
    %         \right)\bar x
    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
    %         \\
    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
    %         + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}\bar x
    %         - \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}} x_{k - 1}
    %         \\
    %         &= \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
    %         + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
    %     \end{align*}
    %     \textbf{proof of \ref{lemma:snapg2-itrs-props-item2}.}
    %     From Definition \ref{def:snapg-v2} it has directly: 
    %     \begin{align*}
    %         z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
    %         \\
    %         &= \alpha_k \bar x + x_{k - 1} - x_k - \alpha_k x_{k - 1}
    %         \\
    %         &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
    %         \\
    %         &= \alpha_k (\bar x - v_k).
    %     \end{align*}

    % \end{proof}
    % % --------------------------------------------------------------------------------------------------------------
    % \begin{theorem}[SNAPG-V2 one step convergence \textcolor{red}{DEPRECATED}]\label{thm:snapg2-one-step}
    %     Let $F$ satisfies assumption \ref{ass:interp-hypothesis}. 
    %     Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} uses this $F$. 
    %     Let $\mathbb E_k$ denotes the expectation conditioned on $I_0, I_1, \ldots, I_{k - 1}$. 
    %     Then, for all $k \ge 1$, it has the following inequality 
    %     \begin{align*}
    %         & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
    %         - F(\bar x) 
    %         + \mathbb E_k\left[
    %             \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %         \right]
    %         \\
    %         &\le 
    %         (1 - \alpha_k)\left(
    %                 \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
    %                 - F(\bar x)
    %                 + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
    %         \right)
    %             \\ &\quad 
    %             + \mathbb E_k\left[
    %                 \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
    %             \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
    %             + \frac{\alpha_k(\tilde\mu - \mu)}{2} 
    %             \Vert \bar x - v_{k - 1}\Vert^2. 
    %     \end{align*}
    %     And for $k = 0$, it has 
    %     \begin{align*}
    %         \mathbb E \left[ F_{I_0}\right] - F(\bar x) 
    %         + \frac{L_0}{2}\mathbb E \left[\Vert \bar x - x_0\Vert^2\right]
    %         &\le 
    %         \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
    %     \end{align*}
    % \end{theorem}
    % \begin{proof}
    %     Let's suppose that $I_k = i$ and, for all $k \ge 0$. 
    %     Let $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$ where $\bar x$ is a minimizer of $F$. 
    %     The proof is long so, we use letters and subscript under relations such as $\underset{(\cdot)}{=}, \underset{(\cdot)}{\ge}$ to indicate which result is used going from the previous expression to the next. 
    %     We list the following intermediate results, (d)-(g) are proved at the end of the proof. 
    %     \begin{itemize}
    %         \item[(a)] We can use proximal gradient inequality from Theorem \ref{thm:pg-ineq} with $z = z_k$ because each $F_i$ is $K_i$ Lipschitz smooth and, $\mu^{(i)}$ strongly convex with $K_i \ge \mu^{(i)}$. 
    %         \item[(b)] We can use Jensen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 
    %         \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right)$. 
    %         \item[(d)] Prove in Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item1} we use the equality:
    %         \begin{align*}
    %             (\forall k \ge 1)\; 
    %             z_k - y_k 
    %             = 
    %             \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
    %             + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1}).
    %         \end{align*}
    %         \item [(e)] From Lemma \ref{lemma:snapg2-itrs-props} \ref{lemma:snapg2-itrs-props-item2}, we use: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
    %         \item [(f)] Using direct algebra, we have for all $k \ge 1$: 
    %         \begin{align*}
    %             \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
    %             - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
    %             = \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
    %             {2\left(L_k - \mu^{(i)}\right)}. 
    %         \end{align*}
    %         \item [(g)] Using (c), we have for all $k \ge 1$: 
    %         \begin{align*}
    %             \frac{\left(
    %                 L_k\alpha_k - \mu^{(i)}
    %             \right)^2}{2(L_k - \mu^{(i)})} 
    %             -
    %             \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} 
    %             = 
    %             \frac{
    %             \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
    %             \left(\alpha_k - 1\right)
    %             }
    %             {2(L_k - \mu^{(i)})}
    %             + \frac{\alpha_k(\tilde \mu_k - \mu^{(i)})}{2}. 
    %         \end{align*}
    %         \item[(h)] Because we assumed interpolation hypothesis in Assumption \ref{ass:interp-hypothesis}, it has $\mathbb E[F_{I_k}(\bar x)] = F(\bar x)$ for all $\bar x$ that is a minimizer of $F$. 
    %     \end{itemize}
    %     For all $k \ge 1$, starting with (a) we have: 
    %     \begin{align}\label{ineq:snapg2-one-step-chain1}
    %         \begin{split}
    %             0 &\le F_i(z_k) - F_i(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
    %             \\
    %             &\underset{\text{(b)}}{\le}
    %             \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) \\
    %                 &\quad 
    %                 - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
    %                 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2. 
    %         \end{split}
    %     \end{align}
    %     And we have the following chain of equalities:
    %     {\allowdisplaybreaks
    %     \begin{align*}
    %         & - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
    %         + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
    %         \\
    %         &\underset{\text{(d)}}{=}
    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
    %             \\&\quad
    %             + \frac{L_k - \mu^{(i)}}{2}
    %             \left\Vert
    %                 \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
    %                 + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1})
    %             \right\Vert^2
    %         \\
    %         &= 
    %         - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
    %             \\&\quad
    %             + \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2 
    %             \\&\quad 
    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
    %         \\
    %         &= 
    %         \left(
    %             \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
    %         \right)\Vert \bar x - x_{k - 1}\Vert^2
    %             \\ &\quad 
    %             + \left(
    %                 \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
    %             \right) \Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %             \\&\quad 
    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
    %         \\
    %         &\underset{\text{(f)}}{=}
    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
    %         {2\left(L_k - \mu^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2
    %             \\ &\quad 
    %             + \left(
    %                 \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
    %             \right) \Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %             \\&\quad 
    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
    %         \\
    %         & \underset{\text{(g)}}{=} 
    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
    %         {2\left(L_k - \mu^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2
    %             \\ &\quad 
    %             + \left(
    %                 \frac{
    %                     \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
    %                     \left(\alpha_k - 1\right)
    %                 }
    %                 {2(L_k - \mu^{(i)})}
    %                 + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2}
    %             \right) 
    %             \Vert \bar x - v_{k - 1}\Vert^2
    %             \\ &\quad 
    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
    %         \\
    %         &= 
    %         \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\left(
    %             \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
    %         \right) 
    %             \\ &\quad 
    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %         \\
    %         &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
    %             \\ &\quad 
    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2.
    %     \end{align*}
    %     }
    %     Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-chain1} it gives: 
    %     {\allowdisplaybreaks
    %     \begin{align*}
    %         0 &\le 
    %         \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
    %             \\&\quad 
    %             - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
    %             \\ &\quad 
    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %         \\
    %         &\underset{\text{(e)}}{=} 
    %         \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
    %             \\&\quad 
    %             - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %             + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
    %             \Vert x_{k - 1} - v_{k - 1} \Vert^2
    %             \\ &\quad 
    %             + \frac{\alpha_k(\tilde\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
    %         \\
    %         &= (\alpha_k - 1)F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) + F_i(\bar x)
    %             \\&\quad 
    %             - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 

>>>>

\newcommand{\cov}{\ensuremath{\operatorname{Cov}}}
\newcommand{\var}{\ensuremath{\operatorname{Var}}}
\newcommand{\expect}{\ensuremath{\mathbb E}}

@@

            \textbf{NOTE}. Contrary to definitions of Bregman Divergence found in the literatures, \textbf{We do not assume} that $D_f(x, y) \iff x = y$. 

@@

            \item Let $(L_k)_{k \ge 0}$ a sequence of strictly positive numbers, 

@@

            \item $\sigma^{(I_k)} \le L_k$ be another list of i.i.d random variable, 
            \item $\tilde \mu \ge 0$ be a constant that is fixed.

@@

            \item $F$ also satisfies Assumption \ref{ass:sum-of-many-aff-comp} with $\RR^{m \times n}$ with matrices: $A^{(1)}, A^{(2)}, \ldots, A^{(n)}$, and vectors $b^{(1)}, \ldots, b^{(n)}$ in $\RR^n$.  

@@

        Then, SNAPG-V2 affine specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions in Definition \ref{def:snapg-v2-aff} with the above parameters. 

@@

        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-aff}. 

@@

            \item $F$ satisfies Assumption \ref{ass:sum-of-many}, which is equivalently to Assumption \ref{ass:sum-of-many-aff-comp} with $A^{(i)} = I$ and, $\nu^{(i)} = \mu^{(i)}$. 

@@

        Then, SNAPG-V2 vanilla specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions in Definition \ref{def:snapg-v2-aff} with the above parameters. 
    \begin{definition}[SNAPG-V2 classical]\label{def:snapg-v2-classical}
        Let $F, (I_k)_{k \ge 0}, \tilde \mu$ and, $(L_k)_{k \ge 0}$ be given as in Definition \ref{def:snapg-v2-aff}. 
            \item Choose $\sigma^{(k)} = 0$. 
            \item Choose $\tilde \mu = 0$. 
        In this case the algorithm simplifies, it can be presented as: 
            & \alpha_k \in (0, 1): (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - /L_k\right), \\
            & y_k = \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}, \\
        Then, SNAPG-V2 classical specifies algorithms that generate the sequence $(y_k, x_k, v_k)_{k \ge 0}$ satisfying conditions in Definition \ref{def:snapg-v2-aff} with the above parameters. 

@@

    \begin{lemma}[SNAPG-V2 one step convergence stage I \textcolor{red}{NEW}]\;\label{lemma:snapg2-one-step-s1}\\

@@

        \begin{align}\label{ineq:snapg2-one-step-s1-rslt1}

@@

        \begin{align}\label{ineq:snapg2-one-step-s1-rslt2}

@@

            \item Assume $x_{k - 1}, v_{k - 1}$ produces the same projection point $\bar x$ onto $\ker A^{(i)}$, i.e: $\bar x = \Pi^{(i)} x_{k - 1} = \Pi^{(i)} v_{k - 1}$. 

@@

            & \mathcal R_k^{(i)} = 
            - \frac{(1 - \alpha_k)\sigma^{(i)}\left(L_k\alpha_k - \sigma^{(i)}\right)}{2\left(L_k - \sigma^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2

@@

        And when $k = 0$, we have \eqref{ineq:snapg2-one-step-s1-rslt2} as well. 

@@

        Firstly take note that from Lemma \ref{lemma:snapg2-one-step-s1} using the fact that $\Pi^{(i)}$ is a projection matrix it has directly: 
        Next, we will show that $\Pi^{(i)}(z_k - y_k), \Pi^{(i)}(\bar x - x_{k - 1})$ are zero under assumptions listed in item (i), (ii). 

@@

        \textbf{Let's prove (i)}. 
        Since $A^{(i)} = I$, its kernel is zero hence the $\Pi^{(i)}$ in Lemma \ref{lemma:snapg2-one-step-s1} projects to $\{0\}$ and the term $\Pi^{(i)}(z_k - y_k) = \mathbf 0$ in \eqref{ineq:snapg2-one-step-s1-rslt1}. It's done. 

@@

        \textbf{Proof of (ii)}. 
        When $\bar x = \Pi^{(i)} x_{k - 1} = \Pi^{(i)} v_{k - 1}$, these three points $v_{k - 1}, x_{k - 1}, \bar x$ are on the same affine span. 
        More importantly, the vector $x_{k - 1} - \bar x \in (\ker A^{(i)})^{\perp}$, and $v_{k - 1} - \bar x \in (\ker A^{(i)})^{\perp}$. 
        Recall that $z_k = \alpha_k \bar x + (1 - \alpha_k) x_{k - 1}$ from Lemma \ref{lemma:snapg2-one-step-s1}, obviously $z_k \perp \ker A^{(i)}$ as well. 
        Therefore, we have: 
            \Pi^{(i)}(\bar x - x_{k - 1}) = \mathbf 0. 
        Next, using Lemma \ref{lemma:iters-snapg2-proto} \ref{lemma:iters-snapg2-proto-item1} it has 
            & \left\Vert
                \Pi^{(i)} \left(
            \right\Vert
                \frac{L_k\alpha_k - \sigma^{(i)}}{L_k - \sigma^{(i)}}\Pi^{(i)}(\bar x - v_{k - 1})
                \frac{\sigma^{(i)}(1 - \alpha_k)}{L_k - \sigma^{(i)}}\Pi^{(i)}(\bar x - x_{k - 1})
            \right\Vert
        The base case $k = 0$ proof is similar to what's in \ref{lemma:snapg2-one-step-s1}. 

@@

    \begin{lemma}[SNAPG-V2 classical one step convergence]\label{lemma:snapg-v2-one-step-not-scnvx}
        Suppose that the sequence $(v_k, x_k, y_k)_{k \ge 0}$ is generated by algorithms that satisfy Definition \ref{def:snapg-v2-classical}, then for all $k \ge 1$, the $\mathcal R^{(i)}_k$ in \eqref{ineq:snapg2-one-step-s1-rslt1} equals to zero. 
        Let $\mathbb E_k$ defines the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}, I_k$. 
        If in addition, Assumption \ref{ass:interp-hypothesis} holds. 
        Then, it has for all $k \ge 1$ the inequality: 
            & \expect_{k - 1}
            \left[
                F_{I_k}(x_k)
                - F(\bar x)
            \right]
                F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2} \Vert \bar x - v_{k - 1}\Vert^2
            \right). 
        and, inequality \ref{ineq:snapg2-one-step-s1-rslt2} holds when $k = 0$. 
        Setting $\sigma^{(i)} = 0$, it has $\mathcal R^{(i)}_k = \alpha_k(\tilde \mu - \sigma^{(i)})/2\Vert \bar x - v_{k - 1}\Vert^2$. 
        By Definition \ref{def:snapg-v2-classical}, $\tilde \mu = 0, \sigma^{(i)} = 0$ for all $i = 1, 2, \ldots, n$, so $\mathcal R^{(i)}_k = 0$ for all $k \ge 1$. 
